Dependent Variable Graphs

### 2022-04-10 combined data set/DVgraphs.Rmd
knitted DV graphs to html

---
title: "Dependent Variable Graphs"
output:
  html_document:
    fig_width: 9
    fig_height: 6
    fig_caption: yes
    keep_md: yes
    theme: paper
    df_print: paged

pdf_document:

    toc: true
    number_sections: true
    toc_depth: 2
    fig_width: 9
    fig_height: 6
    fig_caption: yes
---

@@

```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
moduletwo <- read_excel(here::here("thesis_surveydata/political_factors_complete.xlsx"))
save(moduletwo, file = "moduletwo.rda")

@@

```{r, eval=TRUE}

moduleone <- read_excel(here::here("thesis_surveydata/livelihood_insecurity_complete.xlsx"))
save(moduleone, file = "moduleone.rda")
module1 <- data.frame(moduleone)

@@

```{r, eval =TRUE}
#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
codedmodule1 <- module1 %>%

@@

```{r}

>>>>

---
title: "Dependent Variable Graphs"
output:
  pdf_document:
    toc: yes
    number_sections: yes
    toc_depth: 2
    fig_width: 9
    fig_height: 6
    fig_caption: yes

  html_document:
    fig_width: 9
    fig_height: 6
    fig_caption: yes
    keep_md: yes
    theme: paper
    df_print: paged

---

@@

```{r, echo=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
moduletwo <- read_excel(here::here("thesis_surveydata/political_factors_complete.xlsx"))

@@

```{r, eval=TRUE, echo=FALSE}

moduleone <- read_excel(here::here("thesis_surveydata/livelihood_insecurity_complete.xlsx"))

module1 <- data.frame(moduleone)

@@

```{r, eval =TRUE, echo=FALSE}
#This chunk contains the coding schemes of various scales used in survey one: eco-political factors, kahan scale and acceptance scale
codedmodule1 <- module1 %>%

@@
